Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$

### 2019-12-30 paper.tex
Tweak wording

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

@@

Tips selection requires a stable network connection to wait the response from IOTA full nodes ,and Proof-of-Work (PoW) needs computation power to perform. Figure \ref{fig:mam_send} shows PDF of publishing one message to MAM endpoint for 100 times. The average time for PC to send a message is 48.1069 seconds, and Raspberry Pi 3 takes 743.8586 seconds.

>>>>

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) that allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contracts\cite{smartContract} and cloud servers. Moreover, Ethereum smart contract can also realize the purchase agreement, including authorization and penalization. However, the architecture of DIaaS needs high trust on the CSS. If the CSS is malicious or has crashed, losses to both providers and consumers will result. Also, performance analysis shows that IoT devices have low efficiency interactions with Ethereum due to the time-consuming Proof-of-Work (PoW) process.

@@

Tips selection requires a stable network connection to wait the response from IOTA full nodes, and PoW requires enough computation resources to perform. Figure \ref{fig:mam_send} shows PDF of publishing one message to MAM endpoint for 100 times. The average time for PC to send a message is 48.1069 seconds, and Raspberry Pi 3 takes 743.8586 seconds.
